### 2016-12-01 local-capability-machine.tex
Many things happened. Sorry, Dominique

%Variables
\newcommand{\var}[1]{\mathit{#1}}
\newcommand{\hs}{\var{ms}}
\newcommand{\ms}{\hs}
\newcommand{\hv}{\var{hv}}
\newcommand{\rv}{\var{rv}}
\newcommand{\lv}{\var{lv}}
\newcommand{\gl}{\var{g}}
\newcommand{\pc}{\mathit{pc}}
\newcommand{\pcreg}{\mathrm{pc}}
\newcommand{\addr}{\var{a}}
\newcommand{\offset}{\var{offset}}
\newcommand{\word}{\var{w}}
\newcommand{\start}{\var{base}}
\newcommand{\addrend}{\var{end}}
\newcommand{\pwlv}{\var{pwl}}
\newcommand{\mem}{\var{mem}}
\newcommand{\reg}{\var{reg}}
\newcommand{\heapseg}{\var{ms}}
\newcommand{\heap}{\var{mem}}
\newcommand{\mode}{\var{mode}}
\newcommand{\perm}{\var{perm}}
\newcommand{\permp}{\var{permPair}}
\newcommand{\roll}{\var{roll}}
\newcommand{\instr}{\var{instr}}
\newcommand{\stdcap}[1][(\perm,\gl)]{\left(#1,\start,\addrend,\addr \right)}
\newcommand{\adv}{\var{adv}}
\newcommand{\msframe}{ms_\var{frame}}
\newcommand{\link}{\var{link}}
\newcommand{\stk}{\var{stk}}
\newcommand{\flag}{\var{flag}}
\newcommand{\nwl}{\var{nwl}}
\newcommand{\pwl}{\var{pwl}}
\newcommand{\sta}{\var{sta}}
\newcommand{\cnst}{\var{cnst}}

@@

\newcommand{\revokeTemp}[1]{\plainfun{revokeTemp}{#1}}
\newcommand{\erase}[2]{\floor*{#1}_{\{#2\}}}

@@

\newcommand{\localReg}{\var{localReg}}
\newcommand{\globalReg}{\var{globalReg}}

@@

We will often want to make room in memory for a linking-table capability and a flag-table capability. We therefore define a constant that represents the offset of the actual code of a function caused by these two capabilities:
\[
    \var{offset-link-flag} \defeq 2
\]

@@

\begin{lemma}[Correctness lemma for \texttt{f1}] \forcenewline
\label{lem:correctness-f1}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\var{offset-link-flag}) \\
    c_{f1} & \defeq ((\rwx,\glob),\mathtt{f1}-\var{offset-link-flag},\mathtt{1f},\mathtt{f1}) \\
    c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+\var{offset-link-flag}) \\
    m & \defeq \hs_{f1} \uplus 
               \hs_\flag \uplus                
               \ms_{\var{link}} \uplus 
               \hs_\adv \uplus 
               \ms_{\malloc} \uplus 
               \hs_{\var{frame}} 
  \end{align*}
where 
\begin{align*}
  &\dom(\hs_{f1}) = [\mathtt{f1}-\var{offset-link-flag},\mathtt{1f}] \\
  &\dom(\hs_\flag) = [\flag,\flag] \\
  &\dom(\ms_\link) = [\link,\link+1]\\
  &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
  &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
\end{align*}
and
\begin{itemize}
\item The first address of $\hs_{f1}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f1}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f1}$ contains the code of $f1$.
\item $\ms_\flag = [flag \mapsto 0]$
\item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
\item $\hs_\adv$ contains a global read-only capability for $\hs_\link$ on its first address. The remaining cells of the memory segment only contain instructions.
\end{itemize}
if 
  \[
    (\reg_0\update{\pcreg}{c_{f1}},m) \step[n] (\halted,m'),
  \]
then
\[
  m'(\flag) = 0
\]  
\end{lemma}

@@

\item $c_{\var{ar}}' = ((\entry,\local)b,e,b+\var{offset-link-flag})$ where $b+\var{offset-link-flag}$ is the first address of the activation code.

@@

\begin{lemma}
  \label{lem:correctness-f2}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\var{offset-link-flag}) \\
    c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-\var{offset-link-flag},\mathtt{2f},\mathtt{f2}) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_{\adv},\start_\stk-1) \\
    \reg & \in \Regs \\
    m & \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_{\var{link}} \uplus 
        \hs_\adv \uplus 
        \ms_{\malloc} \uplus 
        \ms_{\var{stk}} \uplus
        \ms_{\var{frame}} 
  \end{align*}
  where 
  \begin{align*}
    &\dom(\hs_{f2}) = [\mathtt{f2}-\var{offset-link-flag},\mathtt{2f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
  \end{align*}
  and
  \begin{itemize}
  \item The first address of $\hs_{f2}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f2}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f2}$ contains the code of $f2$.
  \item $\ms_\flag = [flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\hs_\adv$ is only instructions and possibly a global read-only capability for $\hs_\link$
  \end{itemize}
  if 
  \[
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}
\begin{proof}[Proof of lemma~\ref{lem:correctness-f2}]
  Let $n$ be given and make the assunptions of the lemma. Consider the execution until just after the jump to $\adv$, i.e.,
  \begin{multline*}
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[k] \\
    (\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''},m'')
  \end{multline*}
Where 
\[
  m''  \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_\link \uplus 
        \hs_\adv \uplus 
        \ms_\malloc \uplus 
        \ms_\stk' \uplus
        \ms_{\var{frame}}
\]
Only the stack part of memory has changed. The stack and register-file at this point of execution is illustrated in figure~\ref{fig:f2-stack-before-adv}, where
\begin{itemize}
\item The range of authority for 
  \begin{itemize}
  \item $c_\stk'$ is $[\start_\stk,\addrend_\stk]$ (the entire stack)
  \item $c_\stk''$ is $[\start_\stk'',\addrend_\stk]$ (the unused part of the stack)
  \end{itemize}
  the two stack capabilities have the same permissions as $c_\stk$
\item $c_{f2}'$ points to the return address in f2's code.
\item $c_{\var{prp}}$ is a local enter-capability (with authority of all of the stack).
\item Notice: $f2$ has no return capability, so $r_0$ was not listed as a private register in the call.
\end{itemize}

@@

    \item case $\npair{c_{\var{prp}}} \in \stdvr(W)$:\\

@@

@@

Memory segment satisfaction:
\begin{align*}
  &\heapSat[\hs]{n}{W} 
  \text{ iff }
  \left\{\begin{aligned}
    &\exists R : \dom(\erase{W}{\perma,\temp}) \rightarrow \HeapSegments \ldotp \\
    &\quad \hs = \uplus_{r\in\dom(\erase{W}{\perma,\temp})}R(r) \land \\
    &\quad \forall r \in \dom(\erase{W}{\perma,\temp}) \ldotp\\
    &\qquad \forall n'<n \ldotp \\
    &\qquad \quad \exists H,s \ldotp\\
    &\qquad \qquad W(r) = (\_,s,\_,H) \land \\
    &\qquad \qquad \npair[n']{R(r)} \in H(s)(\xi^{-1}(W))\\
  \end{aligned}\right.
\end{align*}
\dominique{quantification over $n' < n$ needed?}

@@

For convenience define
\begin{align*}
  \localReg(W) & \defeq \dom(\erase{W}{\perm,\temp}) \\
  \globalReg(W) & \defeq \dom(\erase{W}{\perm})
\end{align*}
$\localReg$ are the regions that local capabilities may govern - that is permanent and temporary regions. $\globalReg$ are the regions that global capabilities may govern - that is permanent regions. Now define the following function
\[
  \var{localityReg}(\gl,W) \defeq 
  \begin{cases}
    \localReg(W) & \text{if } \gl = \local \\
    \globalReg(W) & \text{if } \gl = \glob
  \end{cases}
\]

@@

\begin{align*}
    & \writeCond{} : ((\Views \rightharpoonup \Regions) \times \Globals) \fun \Worlds \monnefun \UPred{\Addrs^2}  \\
    & \writeCond{}(\iota,\gl)(W) =  \\
    & \quad \begin{aligned}[t]
              \{ \npair{(\start,\addrend)} \mid & \;\exists r \in \var{localityReg}(g,W) \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nsupsim[n-1] \iota_{\start',\addrend'} \}
            \end{aligned}
\end{align*}

@@

\begin{lemma}[Private monotonicity-like property]
\label{lem:priv-mono-like}
  \begin{align*}
    & \forall \hs, n, W, W' \ldotp \\
    & \quad  \heapSat[\hs]{n}{W} \land W' \futurewk \wrev{W} \futurestr W \\
    & \qquad \Rightarrow \exists \hs', \hs_f \ldotp \hs = \hs' \uplus \hs_f \land \heapSat[\hs']{n}{W'}
  \end{align*}
\end{lemma}

>>>>

%Variables
\newcommand{\var}[1]{\mathit{#1}}
\newcommand{\hs}{\var{ms}}
\newcommand{\ms}{\hs}
\newcommand{\hv}{\var{hv}}
\newcommand{\rv}{\var{rv}}
\newcommand{\lv}{\var{lv}}
\newcommand{\gl}{\var{g}}
\newcommand{\pc}{\mathit{pc}}
\newcommand{\pcreg}{\mathrm{pc}}
\newcommand{\addr}{\var{a}}
\newcommand{\offset}{\var{offset}}
\newcommand{\word}{\var{w}}
\newcommand{\start}{\var{base}}
\newcommand{\addrend}{\var{end}}
\newcommand{\pwlv}{\var{pwl}}
\newcommand{\mem}{\var{mem}}
\newcommand{\reg}{\var{reg}}
\newcommand{\heapseg}{\var{ms}}
\newcommand{\heap}{\var{mem}}
\newcommand{\mode}{\var{mode}}
\newcommand{\perm}{\var{perm}}
\newcommand{\permp}{\var{permPair}}
\newcommand{\roll}{\var{roll}}
\newcommand{\instr}{\var{instr}}
\newcommand{\stdcap}[1][(\perm,\gl)]{\left(#1,\start,\addrend,\addr \right)}
\newcommand{\adv}{\var{adv}}
\newcommand{\msframe}{ms_\var{frame}}
\newcommand{\link}{\var{link}}
\newcommand{\stk}{\var{stk}}
\newcommand{\flag}{\var{flag}}
\newcommand{\nwl}{\var{nwl}}
\newcommand{\pwl}{\var{pwl}}
\newcommand{\sta}{\var{sta}}
\newcommand{\cnst}{\var{cnst}}
\newcommand{\olf}{\var{offsetLinkFlag}}
\newcommand{\prp}{\var{prp}}

@@

\newcommand{\revokeTemp}[1]{\plainfun{revokeTemp}{#1}}
\newcommand{\erase}[2]{\floor*{#1}_{\{#2\}}}
\newcommand{\activeReg}[1]{\plainfun{active}{#1}}

@@

\newcommand{\localityReg}{\var{localityReg}}
\newcommand{\localReg}{\var{localReg}}
\newcommand{\globalReg}{\var{globalReg}}

@@

We will often want to make room in memory for a linking-table capability and a flag-table capability. We therefore define a constant that represents the offset of the actual code of a function caused by these two capabilities:
\[
    \olf \defeq 2
\]

@@

\begin{lemma}[Correctness lemma for \texttt{f1}] \forcenewline
\label{lem:correctness-f1}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\
    c_{f1} & \defeq ((\rwx,\glob),\mathtt{f1}-\olf,\mathtt{1f},\mathtt{f1}) \\
    c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+\olf) \\
    m & \defeq \hs_{f1} \uplus 
               \hs_\flag \uplus                
               \ms_{\var{link}} \uplus 
               \hs_\adv \uplus 
               \ms_{\malloc} \uplus 
               \hs_{\var{frame}} 
  \end{align*}
where 
\begin{align*}
  &\dom(\hs_{f1}) = [\mathtt{f1}-\olf,\mathtt{1f}] \\
  &\dom(\hs_\flag) = [\flag,\flag] \\
  &\dom(\ms_\link) = [\link,\link+1]\\
  &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
  &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
\end{align*}
and
\begin{itemize}
\item The first address of $\hs_{f1}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f1}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f1}$ contains the code of $f1$. \dominique{why not write this in symbols?}
\item $\ms_\flag = [flag \mapsto 0]$
\item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
\item $\hs_\adv$ contains a global read-only capability for $\hs_\link$ on its first address. The remaining cells of the memory segment only contain instructions.
\end{itemize}
if 
  \[
    (\reg_0\update{\pcreg}{c_{f1}},m) \step[n] (\halted,m'),
  \]
then
\[
  m'(\flag) = 0
\]  
\end{lemma}

@@

\item $c_{\var{ar}}' = ((\entry,\local)b,e,b+\olf)$ where $b+\olf$ is the first address of the activation code.

@@

\begin{lemma}[Correctness lemma for \texttt{f2}]
  \label{lem:correctness-f2}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\
    c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-\olf,\mathtt{2f},\mathtt{f2}) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_{\adv},\start_\stk-1) \\
    \reg & \in \Regs \\
    m & \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_{\var{link}} \uplus 
        \hs_\adv \uplus 
        \ms_{\malloc} \uplus 
        \ms_{\var{stk}} \uplus
        \ms_{\var{frame}} 
  \end{align*}
  where 
  \begin{align*}
    &\dom(\hs_{f2}) = [\mathtt{f2}-\olf,\mathtt{2f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
  \end{align*}
  and
  \begin{itemize}
  \item The first address of $\hs_{f2}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f2}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f2}$ contains the code of $f2$.
  \item $\ms_\flag = [flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\hs_\adv$ is only instructions and possibly a global read-only capability for $\hs_\link$
  \end{itemize}
  if 
  \[
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}
\begin{proof}[Proof of lemma~\ref{lem:correctness-f2}]
  Let $n$ be given and make the assunptions of the lemma. Consider the execution until just after the jump to $\adv$, i.e.,
  \begin{multline*}
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[k] \\
    (\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''},m'')
  \end{multline*}
Where 
\[
  m''  \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_\link \uplus 
        \hs_\adv \uplus 
        \ms_\malloc \uplus 
        \ms_\stk' \uplus
        \ms_{\var{frame}}
\]
Only the stack part of memory has changed. The stack and register-file at this point of execution is illustrated in figure~\ref{fig:f2-stack-before-adv}, where
\begin{itemize}
\item The range of authority for 
  \begin{itemize}
  \item $c_\stk'$ is $[\start_\stk,\addrend_\stk]$ (the entire stack)
  \item $c_\stk''$ is $[\start_\stk'',\addrend_\stk]$ (the unused part of the stack)
  \end{itemize}
  the two stack capabilities have the same permissions as $c_\stk$
\item $c_{f2}'$ points to the return address in f2's code.
\item $c_{\var{prp}}$ is a local enter-capability (with authority of all of the stack).
\item Notice: $f2$ has no return capability, so $r_0$ was not listed as a private register in the call.
\end{itemize}

@@

    \item case $\npair{c_{\var{prp}}} \in \stdvr(W)$: \label{f2:c-prp}\\

@@

\begin{lemma}[Correctness lemma for \texttt{f3}]
    \label{lem:correctness-f3}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\
    c_{f3} & \defeq ((\rwx,\glob),\mathtt{f3}-\olf,\mathtt{3f},\mathtt{f3}) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_{\adv},\start_\stk-1) \\
    \reg & \in \Regs \\
    m & \defeq \hs_{f3} \uplus 
        \hs_\flag \uplus                
        \ms_{\var{link}} \uplus 
        \hs_\adv \uplus 
        \ms_{\malloc} \uplus 
        \ms_{\var{stk}} \uplus
        \ms_{\var{frame}} 
  \end{align*}
  where 
  \begin{align*}
    &\dom(\hs_{f3}) = [\mathtt{f3}-\olf,\mathtt{3f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
  \end{align*}
  and
  \begin{itemize}
  \item The first address of $\hs_{f3}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f3}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f3}$ contains the code of $f3$.
  \item $\ms_\flag = [flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\hs_\adv$ contains a read-write capability for $\hs_\link$ on its first address and otherwise it consists only of code.
  \end{itemize}
  if 
  \[
    (\reg\update{\pcreg}{c_{f3}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}

\begin{proof}[Proof of Lemma~\ref{lem:correctness-f3}]
This proof goes like the proof of Lemma~\ref{lem:correctness-f3} except for item \ref{f2:c-prp}
\begin{enumproof}[start=3]
  \item $\npair{\reg_0\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''}} \in \stdrr(W)$ \\
    $\dots$
  \begin{enumproof}[start=3]
  \item $\npair{c_{\var{prp}}} \in \stdvr(W)$ \\
    To this end let $n' < n$ and $W' \futurewk W$ be given and show
    \[
      \npair[n']{\updatePcPerm(c_\prp)} \in \stder(W')
    \]
    to this end let 
    \begin{enumproof}
      \item $n'' \leq n'$
      \item $\npair[n'']{\reg} \in \stdrr(W')$ \label{f3:mem-sat-mid}
      \item $\heapSat[\ms]{n''}{W'}$
    \end{enumproof}
    be given and show
    \[
      \npair[n'']{(\reg\update{\pcreg}{\updatePcPerm(c_\prp)},\ms)}
    \]
    to this end let $i \leq n''$, $\ms_f$, and $m''$ be given and assume
    \begin{enumproof}[resume]
      \item $(\reg\update{\pcreg}{c_\prp},\ms \uplus \ms_f) \step[i] (\halted,m'')$ \label{f3:mid-exec}
    \end{enumproof}
    now show
    \[
      \exists \ms_R,\ms', W'' \futurestr W' \ldotp m'' = \ms' \uplus \ms_R \uplus \ms_f \land \heapSat[\ms']{n''-i}{W''}
    \]
    At this point use Lemma~\ref{lem:priv-mono-like2} with \ref{f3:mem-sat-mid} to get $\ms_p$, $\ms_r$, and $R$ that such that $\ms = \ms_p \uplus \ms_r$ and $\heapSat[\ms_p]{n''}{W'}$. We can further conclude that $\ms |_{[\start_\stk,\addrend_\stk]} \subseteq \ms_r$ \lau{The needs to be spelled out - preferably in an easy to use lemma. The idea is that $R$ partitions $\ms_r$ into memory segments that each are accepted by a temporary region. The stack is governed by a temporary region, so it must be in $\ms_r$.}.

 Now consider the first steps of execution \ref{f3:mid-exec}. From \ref{f3:mem-sat-mid} we have that the private part of the stack and $f3$ is unchanged, so the recovery code gets to run which restores the stack capability and program counter, and pops the return code off the stack (there are no ``private'' registers). Next, the top word is popped off the stack. Again due to memory satisfaction, we know that this word is the integer 1 and therefore the assertion succeeds. Execution continues by pushing 2 to the stack. Now due the $\mathtt{scall}$ up to the point just after the jump to $\adv$. Figure~\ref{fig:f3-stack-before-snd-adv} shows the stack and register file at this point. The $\ms_p$ part of $\ms$ was not changed. For convenience, name the stack part of memory at this point $\ms'_\stk$.

Let $W^{(3)} = \revokeTemp{W''}\update{i_1}{\iota^\sta(\temp,\ms|_{[\start_\stk, \start_\stk''-1]})}\update{i_2}{\iota^\sta(\temp,\ms|_{[\start_\stk'',\addrend_\stk]})}$

\begin{figure}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   &         \\
   & $\vdots$ \\
\cline{2-2}
$\start_\stk'':$   & $0$\\
\cline{2-2}
$c_\stk',c_\stk'' \rightarrow$   & $c_\stk'$ \\
\cline{2-2}
   & $c_{f2}'$ \\
\cline{2-2}
$c_{\var{prp}} \rightarrow$   & Restore code \\
   & $\vdots$ \\
\cline{2-2}
   & $2$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r |c |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $\updatePcPerm{c_\adv}$\\
\cline{2-2}
$r_0$  &  $c_{\var{prp}}$ \\
\cline{2-2}
$r_1$ & $c_\adv$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}'$ \\
\cline{2-2}
& $0$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{Stack and register-file just after second jump to $\adv$.}
\label{fig:f3-stack-before-snd-adv}
\end{figure}
  \end{enumproof}
\end{enumproof}
\end{proof}

@@

Define the function $\active{}$ as follows
\begin{align*}
  \activeReg{} & : \Worlds \fun 2^\RegionNames \\
  \activeReg{W} & \defeq \dom(\erase{W}{\perma,\temp})
\end{align*}

Memory segment satisfaction:
\begin{align*}
  &\heapSat[\hs]{n}{W} 
  \text{ iff }
  \left\{\begin{aligned}
    &\exists R : \activeReg{W} \rightarrow \HeapSegments \ldotp \\
    &\quad \hs = \biguplus_{r\in\activeReg{W}}R(r) \land \\
    &\quad \forall r \in \activeReg{W} \ldotp\\
    &\qquad \forall n'<n \ldotp \\
    &\qquad \quad \exists H,s \ldotp\\
    &\qquad \qquad W(r) = (\_,s,\_,H) \land \\
    &\qquad \qquad \npair[n']{R(r)} \in H(s)(\xi^{-1}(W))\\
  \end{aligned}\right.
\end{align*}
\dominique{quantification over $n' < n$ needed?}

@@

For convenience define
\[
  \localityReg(\gl,W) \defeq 
  \begin{cases}
    \dom(\erase{W}{\perm,\temp}) & \text{if } \gl = \local \\
    \dom(\erase{W}{\perm}) & \text{if } \gl = \glob
  \end{cases}
\]
$\localityReg(\local,W)$ are the regions that local capabilities may govern - that is permanent and temporary regions. $\localityReg(\glob,W)$ are the regions that global capabilities may govern - that is permanent regions. Now define the following function

@@

\begin{align*}
    & \writeCond{} : (\Regions \times \Globals) \fun \Worlds \monnefun \UPred{\Addrs^2}  \\
    & \writeCond{}(\iota,\gl)(W) =  \\
    & \quad \begin{aligned}[t]
              \{ \npair{(\start,\addrend)} \mid & \;\exists r \in \var{localityReg}(g,W) \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nsupsim[n-1] \iota_{\start',\addrend'} \}
            \end{aligned}
\end{align*}

\begin{align*}
    & \readCond{} : \Globals \fun \Worlds \monnefun \UPred{\Addrs^2}  \\
    & \readCond{}(\gl)(W) =  \\
    & \quad \begin{aligned}[t]
              \{ \npair{(\start,\addrend)} \mid & \;\exists r \in \var{localityReg}(g,W) \ldotp \\
              & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
              & \;\qquad W(r)\nsubsim[n-1] \iota_{\start',\addrend'}^\pwl \}
            \end{aligned}
\end{align*}

@@

\begin{lemma}[Revoke temporary memory satisfaction]
\label{lem:priv-mono-like}
  \begin{align*}
    &      \forall \hs, n, W, W' \ldotp \\
    & \quad  \heapSat[\hs]{n}{W} \Rightarrow\\
    & \qquad \exists \hs', \hs_r \ldotp \\
    & \qquad \quad \hs = \hs' \uplus \hs_r \land \heapSat[\hs']{n}{\wrev{W}}
  \end{align*}
\end{lemma}

\begin{lemma}[Revoke temporary memory satisfaction 2]
\label{lem:priv-mono-like2}
  \begin{align*}
    & \forall \ms, n, W \ldotp \heapSat[\ms]{n}{W} \Rightarrow \\
    & \quad \exists \ms', \ms_r, R : \dom(\erase{W}{\temp}) \fun \MemSegments \ldotp \\
    & \qquad \ms = \ms' \uplus \ms_r \land \\
    & \qquad \heapSat[\ms']{n}{\wrev{W}} \land \\
    & \qquad \forall r \ldotp \forall n' < n \ldotp \npair[n']{R(r)} \in W(r).\mathrm{H}(W(r).\mathrm(s))(W)\\
    & \qquad \ms_r = \biguplus_{r \in \dom(R)} R(r)
  \end{align*}
\end{lemma}

\begin{lemma}[Disjoint memory satisfaction]
\label{lem:disj-mem-sat}
  \begin{align*}
    & \forall n \ldotp \forall \ms, \ms' \ldotp \forall W, W' \ldotp\\
    & \quad \heapSat[\ms \uplus \ms' ]{n}{W \uplus W'}
  \end{align*}
\end{lemma}
